<<<<<<< HEAD
Reproducible Research - Homework #1
=======================================

## Loading and preprocessing the data

### Load the data

```{r}
temp <- tempfile()
setInternet2(use=TRUE)
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp,mode="wb")
data <- read.csv(unz(temp,"activity.csv"),header=TRUE, na.strings = "NA")
unlink(temp)
```

### Process/transform the data

Convert the 'date' from characters into POSIXct date format

```{r}
library(lubridate)
data$date <- ymd(data$date)
```

## What is mean total number of steps taken per day?

### Calculate the total number of steps taken per day

```{r}
library(plyr)
# Remove NA values
dat <- data[complete.cases(data),]
s_d <- ddply(dat,"date",summarise,sum=sum(steps))
```
### Display histogram of total steps per day
```{r}
hist(s_d$sum,xlab="# of Steps",ylab="# of Days",
     main="Total Number of Steps Taken Each Day")
```

### Calculate mean and median of total number of steps taken per day
```{r}
summary(s_d$sum)
```

## What is the average daily activity pattern?
### Display a time series plot of the 5-minute interval  and the average number of steps taken, averaged across all days

```{r}
# Find the average number of steps per interval across all days
s_m <- ddply(dat,"interval",summarise,avg=mean(steps))
plot(s_m,type="l",xlab="Interval",ylab="Average # of Steps",
     main="Average Number of Steps by 5 min Interval, Averaged over all days")
```

### Identify Which 5-minute interval contains the maximum number of steps

```{r}
s_m[which.max(s_m$avg),1]
```
## Imputing missing values

### Calculate and report the total number of missing values in the dataset

```{r}
sum(is.na(data$steps))
```

### Replace all of the missing values in the dataset with the average for that 5-minute interval

```{r}
# Add interval average column to dataframe
dat2 <- join(data,s_m,by="interval")
dat2$steps[is.na(dat2$steps)] <- dat2$avg[is.na(dat2$steps)]
```

### Make a histogram of the total number of steps taken each day and Calculate and report the mean and median
```{r}
s_d2 <- ddply(dat2,"date",summarise,sum=sum(steps))
hist(s_d2$sum,xlab="# of Steps",ylab="# of Days",
     main="Total Number of Steps Taken Each Day with NA Replacement")

summary(s_d2$sum)
```

Replacing the NAs with the interval average value caused the number of days with 10,000-15,000 steps to increase (25-35). The Mean was the same for both datasets, but the Median was larger when the NAs were replaced (rather than removed).

## Are there differences in activity patterns between weekdays and weekends?

### Create a new factor variable in the dataset with two levels - "weekday" and "weekend"

```{r}
dat2$Day <- weekdays(dat2$date)
dat2$Day[dat2$Day=="Monday"] <- "weekday"
dat2$Day[dat2$Day=="Tuesday"] <- "weekday"
dat2$Day[dat2$Day=="Wednesday"] <- "weekday"
dat2$Day[dat2$Day=="Thursday"] <- "weekday"
dat2$Day[dat2$Day=="Friday"] <- "weekday"
dat2$Day[dat2$Day=="Saturday"] <- "weekend"
dat2$Day[dat2$Day=="Sunday"] <- "weekend"
```

### Make a panel plot containing a time series plot of the 5-minute interval and the average number of steps taken, averaged across all weekday days or weekend days

```{r}
library(ggplot2)
s_m2 <- ddply(dat2,.(interval,Day),summarise,avg=mean(steps))
ggplot(s_m2,aes(interval,avg))+geom_line()+facet_grid(Day~.)+
  xlab("Interval")+ylab("Average # of Steps")+
  ggtitle("Average Number of Steps by 5 min Interval, with NA replacement")
```
=======
---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
>>>>>>> 80edf39c3bb508fee88e3394542f967dd3fd3270
